Growth model analysis 3spp WB

### 2018-12-12 manuscriptAnalysis/MS_Analysis_3spp_WB.Rmd
added graphs for sens analysis

```{r RI across occ - use this for paper GROWTH RATE}

@@

ageForRI <-  'yoy' #'yoy' or 'adult'
occs <- if (ageForRI == 'yoy') 1:2 else 3:10
indepVarVals <- c(-1.5,0,1.5) # make sure symetrical around 0
indepVars <- c('temp', 'flow', 'temp:flow', 'bkt', 'bnt', 'ats', 'bkt:bnt')
rIBKTBNT <- NULL
# loop over occs
for(rep in 1:simData$nReps){

@@

@@

```{r RI by occ - not used for paper GROWTH}

# make figures of relative importance for each sampling occasion
rIAll <- cAll <- NULL
for( occSelected in 1:(simData$nOcc - 1)){
  print(occSelected)
  lmAll <- ggRIAll <- relImpAll <- coefsAll <- list()

      lmAll[[spp1]] <- lm( grMean ~ temp + flow + temp * flow + temp^2 + flow^2 + bkt + bnt + ats + bnt * bkt, data = grStats3Spp[[spp1]][[1]] %>% filter(occ == occSelected, temp %in% indepVarVals, flow %in% indepVarVals, bkt %in% indepVarVals, bnt %in% indepVarVals, ats %in% indepVarVals))
  #stats3Spp[[spp1]][[1]] %>% filter(occ == occSelected)

@@

  # make bar chart of relative importance of each variable for each spp
  rI <- cbind(data.frame(bktRI = relImpAll[['bkt']]$lmg), 
              data.frame(bntRI = relImpAll[['bnt']]$lmg)) %>%
        rownames_to_column() %>% 
        gather(key=rowname) %>% 
        mutate(var = rep(1:length(relImpAll[['bkt']]$lmg),length(spp)),
               occ = occSelected,
               season = simData$seasons[occSelected])

@@

  rIAll$age <- ifelse(rIAll$occ %in% 1:2, 0, ifelse(rIAll$occ %in% 3:6, 1, 2))

  ggplot(rI, aes(factor(var),value, fill = factor(rowname, levels = c('bktRI','bntRI'), ordered = TRUE))) +
    geom_col(position='dodge') +
    scale_x_discrete('Parameter',
                     labels = c('1' = 'Temp','2' = 'Flow','3' = 'Bkt','4' = 'Bnt','5' = 'Ats','6' = 'Temp*Flow', '7' = "Bkt*Bnt")) +
    scale_fill_grey() +
    scale_y_continuous('Relative proportion of variance explained') +
    ggtitle(paste0("occ = ",occSelected,"  Season = ",simData$seasons[occSelected])) +
    theme_publication() +
    theme( legend.position = 'none')

  # coefficients
  coefs <- cbind(data.frame(bktC = coefsAll[['bkt']]), 
                 data.frame(bntC = coefsAll[['bnt']])) %>%
        rownames_to_column() %>% 
        gather(key=rowname) %>% 
        mutate(var = rep(1:length(coefsAll[['bkt']]),length(spp)),
               occ = occSelected,
               season = simData$seasons[occSelected])

@@

ggplot(rIAll %>% filter(rowname %in% c('bktRI','bntRI')), aes((occ), value, color = factor(rowname))) +
  geom_point() +
  geom_line() +
  geom_vline(xintercept = 2.5) +
  scale_x_continuous('Sampling occasion',
                    breaks = 1:9,
                    labels = c('Autumn','Winter','Spring','Summer', 'Autumn','Winter','Spring','Summer', 'Autumn')
                    ) +
  scale_y_continuous('Relative proportion of variance explained') +
  theme_publication() +
  theme(axis.text.x  = element_text(angle=90, vjust=0.25, size=10)) +
  facet_wrap(~ var, labeller=labeller(var = labels))

ggsave(paste0('figures/3Spp_WB/relImpOccAll_GR.png'), width = 11, height = 9, units='in')

rIAllMinus <- rIAll %>% mutate(value2 = ifelse(rowname == 'bktRI',value * -1, value))
labelsSeason <- c('1'='Autumn','2'='Winter','3'='Spring','4'='Summer','5'='Autumn','6'='Winter','7'='Spring','8'='Summer','9'='Autumn')
labelsSeason2 <- c('1'='Spring','2'='Summer','3'='Autumn','4'='Winter')

ggplot(rIAllMinus, aes(var, y = value2, fill = rowname)) +
  geom_col() +
  coord_flip() +
  scale_x_reverse('Variable', 
                     breaks = 1:7,
                     labels = c('Temp', 'Flow', 'Bkt', 'Bnt','Ats','Temp*Flow',  "Bkt*Bnt")) +
  scale_y_continuous('Relative proportion of variance explained',
                     breaks = c(-1.0, -0.5, 0.0, 0.5),
                     labels = c('1.0', '0.5', '0.0', '0.5')) +
  theme_publication() +
  scale_fill_grey(start = 0.15, end = 0.75) +
  facet_grid(season ~ age, labeller=labeller(season = labelsSeason2))

>>>>

```{r RI across all - use this for paper GROWTH RATE}

@@

indepVarVals <- c(-1.5,0,1.5) # make sure symetrical around 0
indepVars <- c('temp', 'flow', 'temp:flow', 'bkt', 'bnt', 'ats', 'bkt:bnt')
rIBKTBNTAll <- NULL
# loop over occs
for(rep in 1:simData$nReps){

  datOccBKTAll <- grStats3Spp[['bkt']][[1]] %>% filter(iter == rep, temp %in% indepVarVals, flow %in% indepVarVals, bkt %in% indepVarVals, bnt %in% indepVarVals, ats %in% indepVarVals)
  lmAllBKT <- lm( grMean ~ temp + flow + temp * flow + temp^2 + flow^2 + bkt + bnt + ats + bnt * bkt + occ, data = datOccBKTAll) 
  relImpAllBKT <- calc.relimp(lmAllBKT, type = c("lmg"), rela = TRUE)

  datOccBNTAll <- grStats3Spp[['bnt']][[1]] %>% filter(iter == rep, temp %in% indepVarVals, flow %in% indepVarVals, bkt %in% indepVarVals, bnt %in% indepVarVals, ats %in% indepVarVals)
  lmAllBNT <- lm( grMean ~ temp + flow + temp * flow + temp^2 + flow^2 + bkt + bnt + ats + bnt * bkt + occ, data = datOccBNTAll)
  relImpAllBNT <- calc.relimp(lmAllBNT, type = c("lmg"), rela = TRUE)

  rIBKTBNTAll <- rbind(rIBKTBNTAll, data.frame(cbind(rBKT,rBNT)) %>% 
                      rownames_to_column() %>% 
                      gather(key = rowname) %>% 
                      mutate(var = rep(1:length(indepVars),2),
                             varText = rep(names(rBKT),2),
                             iter = rep)
                    )
}

rIBKTBNTAllMeans <- rIBKTBNTAll %>%
  group_by(rowname, var) %>%
  summarise(rIMean = mean(value),
            rISd = sd(value),
            rIUpperCI = quantile(value, 0.95))

dodge <- position_dodge(width=0.9)
ggplot(rIBKTBNTAllMeans, aes(factor(var),rIMean, fill = factor(rowname, levels = c('rBKT','rBNT'), ordered = TRUE))) +
  geom_errorbar(aes(ymin = rIMean - 0.001, ymax = rIUpperCI), width = 0.25, position=dodge) +
  geom_col(position=dodge) +
  scale_x_discrete('Parameter',
                   labels = c('1' = 'Temperature','2' = 'Flow','3' = 'Bkt','4' = 'Bnt','5' = 'Ats','6' = 'Temp*Flow', '7' = "Bkt*Bnt")) +
  scale_fill_grey() +
  scale_y_continuous('Relative proportion of variance explained') +
  theme_publication() +
  geom_hline(yintercept = 0) +
  theme( legend.position = 'none')

ggsave(paste0('figures/3Spp_WB/relImpOccMeanModAll_GR_N',simData$nReps,'.png'), width = 9, height = 7, units='in')

# for MS
rIBKTBNTAllMeans
#    rowname   var  rIMean    rISd rIUpperCI
#    <chr>   <int>   <dbl>   <dbl>     <dbl>
#  1 rBKT        1 0.132   0.0251     0.170 
#  2 rBKT        2 0.670   0.0369     0.731 
#  3 rBKT        3 0.0116  0.0118     0.0330
#  4 rBKT        4 0.0346  0.0256     0.0703
#  5 rBKT        5 0.0951  0.0284     0.140 
#  6 rBKT        6 0.0441  0.0263     0.0919
#  7 rBKT        7 0.0121  0.0155     0.0410
#  8 rBNT        1 0.106   0.0212     0.141 
#  9 rBNT        2 0.568   0.0364     0.623 
# 10 rBNT        3 0.0885  0.0223     0.124 
# 11 rBNT        4 0.00518 0.00556    0.0163
# 12 rBNT        5 0.122   0.0285     0.169 
# 13 rBNT        6 0.0314  0.0176     0.0624
# 14 rBNT        7 0.0782  0.0270     0.122

rIBKTBNTAll %>%
  mutate(isEnvVar = ifelse(varText %in% c('temp','flow','temp:flow'), 1,0)) %>%
  group_by(rowname,isEnvVar) %>%
  summarize(meanMean = mean(value),
            sumMean = sum(value),
            sdMean = sd(value))

#   rowname isEnvVar meanMean sumMean sdMean
#   <chr>      <dbl>    <dbl>   <dbl>  <dbl>
# 1 rBKT           0   0.0383    15.3 0.0402
# 2 rBKT           1   0.282     84.7 0.279 
# 3 rBNT           0   0.0736    29.4 0.0484
# 4 rBNT           1   0.235     70.6 0.239

#bkt
.282/(.282+.038) # 0.88125
#bnt
.235/(.235+.074) # 0.7605178
.881/.76 # 1.159211
```

```{r RI across yoy/adults - use this for paper GROWTH RATE}

ageForRI <-  'yoy' #'yoy' or 'adult'
occs <- if (ageForRI == 'yoy') 1:3 else 4:10
indepVarVals <- c(-1.5,0,1.5) # make sure symetrical around 0
indepVars <- c('temp', 'flow', 'temp:flow', 'bkt', 'bnt', 'ats', 'bkt:bnt')
rIBKTBNT <- NULL
# loop over occs
for(rep in 1:simData$nReps){

@@

#    rowname   var  rIMean    rISd rIUpperCI
#    <chr>   <int>   <dbl>   <dbl>     <dbl>
#  1 rBKT        1 0.516   0.0639     0.619 
#  2 rBKT        2 0.123   0.0332     0.175 
#  3 rBKT        3 0.0209  0.0222     0.0568
#  4 rBKT        4 0.0579  0.0307     0.100 
#  5 rBKT        5 0.193   0.0487     0.273 
#  6 rBKT        6 0.0539  0.0374     0.126 
#  7 rBKT        7 0.0362  0.0303     0.0889
#  8 rBNT        1 0.154   0.0566     0.253 
#  9 rBNT        2 0.0106  0.00999    0.0281
# 10 rBNT        3 0.140   0.0479     0.208 
# 11 rBNT        4 0.00421 0.00467    0.0135
# 12 rBNT        5 0.463   0.0780     0.598 
# 13 rBNT        6 0.173   0.0676     0.294 
# 14 rBNT        7 0.0547  0.0340     0.121

# get isEnvVar sens for yoy and adults - need to rerun the above code for each age
rIBKTBNT %>%
  mutate(isEnvVar = ifelse(varText %in% c('temp','flow','temp:flow'), 1,0)) %>%
  group_by(rowname,isEnvVar) %>%
  summarize(meanMean = mean(value),
            sumMean = sum(value),
            sdMean = sd(value)) %>%
  mutate(age = ageForRI)

#   rowname isEnvVar meanMean sumMean sdMean age  
#   <chr>      <dbl>    <dbl>   <dbl>  <dbl> <chr>
# 1 rBKT           0   0.0769    30.8 0.0763 yoy  
# 2 rBKT           1   0.231     69.2 0.209  yoy  
# 3 rBNT           0   0.165     66.2 0.185  yoy  
# 4 rBNT           1   0.113     33.8 0.0888 yoy

#   rowname isEnvVar meanMean sumMean sdMean age  
#   <chr>      <dbl>    <dbl>   <dbl>  <dbl> <chr>
# 1 rBKT           0   0.0287    11.5 0.0272 adult
# 2 rBKT           1   0.295     88.5 0.377  adult
# 3 rBNT           0   0.0411    16.4 0.0285 adult
# 4 rBNT           1   0.279     83.6 0.343  adult

# ratio of env/(env+spp) means - yoy
.231/(.231 + .0769) # bkt 0.7502436
.165/(.165 + .113) # bnt 0.5935252

# ratio of env/(env+spp) means - adult
.295/(.295 + .0287) # bkt 0.9113377
.279/(.279 + .0411) # bnt 0.8716026

.75/.593 # 1.26
.911/.872 # 1.04
##############################################################
############################################################

@@

```{r RI by occ - use for paper GROWTH}

# make figures of relative importance for each sampling occasion
rIAll <- cAll <- NULL

for(ageGroupLoop in 0:1){
  for(seasonLoop in 1:4){
#for( occSelected in 1:(simData$nOcc - 1)){
  if(ageGroupLoop == 0 & seasonLoop == 2) next

  lmAll <- ggRIAll <- relImpAll <- coefsAll <- list()

  for(spp1 in spp){
    print(c(ageGroupLoop, seasonLoop, spp1))

    datAgeGroupSeason <- grStats3Spp[[spp1]][[1]] %>%
         mutate(ageGroup = ifelse(occ %in% 1:3, 0, 1),
         season = rep(c(3,4,1,2,3,4,1,2,3,4), nrow(grStats3Spp[[spp1]][[1]])/simData$nOcc))

      lmAll[[spp1]] <- lm( grMean ~ temp + flow + temp * flow + temp^2 + flow^2 + bkt + bnt + ats + bnt * bkt, data = datAgeGroupSeason %>% filter(ageGroup == ageGroupLoop, season == seasonLoop, temp %in% indepVarVals, flow %in% indepVarVals, bkt %in% indepVarVals, bnt %in% indepVarVals, ats %in% indepVarVals))

@@

  # make bar chart of relative importance of each variable for each spp
  rI <- cbind(data.frame(bktRI = relImpAll[['bkt']]$lmg), 
              data.frame(bntRI = relImpAll[['bnt']]$lmg)) %>%
        rownames_to_column() %>% 
        gather(key=rowname) %>% 
        mutate(var = rep(1:length(relImpAll[['bkt']]$lmg),length(spp)),
               ageGroup = ageGroupLoop,
               season = seasonLoop)

@@

  #rIAll$age <- ifelse(rIAll$occ %in% 1:2, 0, ifelse(rIAll$occ %in% 3:6, 1, 2))

  }  
}

@@

# ggplot(rIAll %>% filter(rowname %in% c('bktRI','bntRI')), aes((occ), value, color = factor(rowname))) +
#   geom_point() +
#   geom_line() +
#   geom_vline(xintercept = 2.5) +
#   scale_x_continuous('Sampling occasion',
#                     breaks = 1:9,
#                     labels = c('Autumn','Winter','Spring','Summer', 'Autumn','Winter','Spring','Summer', 'Autumn')
#                     ) +
#   scale_y_continuous('Relative proportion of variance explained') +
#   theme_publication() +
#   theme(axis.text.x  = element_text(angle=90, vjust=0.25, size=10)) +
#   facet_wrap(~ var, labeller=labeller(var = labels))
# 
# ggsave(paste0('figures/3Spp_WB/relImpOccAll_GR.png'), width = 11, height = 9, units='in')

rIAllMinus <- rIAll %>% mutate(value2 = ifelse(rowname == 'bktRI',value * -1, value))

labelsSeason <- c('1'='Autumn','2'='Winter','3'='Spring','4'='Summer','5'='Autumn','6'='Winter','7'='Spring','8'='Summer','9'='Autumn')
labelsSeason2 <- c('1'='Spring','2'='Summer','3'='Autumn','4'='Winter')
labelAge <- c('0' = 'Growth year 0/1', '1' = 'Growth Year 1+')

ggplot(rIAllMinus, aes(var, y = value2, fill = rowname)) +
  geom_col() +
  coord_flip() +
  scale_x_reverse('Variable', 
                     breaks = 1:7,
                     labels = c('Temp', 'Flow', 'Bkt', 'Bnt','Ats','Temp*Flow',  "Bkt*Bnt")) +
  scale_y_continuous('Relative proportion of variance explained',
                     breaks = c(-1.0, -0.5, 0.0, 0.5),
                     labels = c('1.0', '0.5', '0.0', '0.5')) +
  theme_publication() +
  scale_fill_grey(start = 0.15, end = 0.75) +
  facet_grid(season ~ ageGroup, labeller=labeller(season = labelsSeason2, ageGroup = labelAge))
